### 2018-12-08 Sections/errors_in_quantum_networks.tex
minor
fixed cat state loss

%Consider an even-parity cat state, as per Eq.~(\ref{eq:cat_state_enc}). Subjecting this to a loss channel yields the mixed state,
%\begin{align}
%&\hat\rho_\mathrm{loss} = \mathcal{E}_\eta^\mathrm{loss}(\ket{\mathrm{cat}_+(\alpha)}\bra{\mathrm{cat}_+(\alpha)}) = {\mathcal{N}_+}^2 \nonumber\\
%&\cdot (\ket{\eta\alpha}\bra{\eta\alpha} + \ket{\eta\alpha}\bra{-\eta\alpha} + \ket{-\eta\alpha}\bra{\eta\alpha}+\ket{-\eta\alpha}\bra{-\eta\alpha}),
%\end{align}
%which has purity,
%\begin{align}
%	\mathcal{P} &= \mathrm{tr}({\hat\rho_\mathrm{loss}}^2)\nonumber\\
%	&=
%\end{align}

%\comment{To do}

@@

A qubit dephasing channel is often quoted in terms of its $T_2$-time, a characteristic time for dephasing to occur under continuous time-evolution. Specifically, the probability of no dephasing occurring scales as,
\begin{align}
p_\mathrm{no\,error} = e^{-t/T_2},	
\end{align}
yielding a the equivalent dephasing channel,
\begin{align}
\mathcal{E}_t^\mathrm{dephasing}(\hat\rho) = e^{-t/T_2} \hat\rho + \frac{1}{2}(1-e^{-t/T_2})(\hat\rho + \hat{Z}\hat\rho\hat{Z}),
\end{align}
as shown in Fig.~\ref{fig:T2_time}. This is equivalent to adding a factor of $e^{-t/T_2}$ to the two off-diagonal (coherence) elements of a qubit's density matrix,
\begin{align}
	\hat\rho_t = \left(\begin{matrix}{}
 \alpha & e^{-t/T_2}\gamma \\
 e^{-t/T_2}\gamma^* & \beta
\end{matrix}\right).
\end{align}

@@

The degree of amplitude damping is often quoted in terms of a channel's $T_1$-time, characterising the expected time for the excited state to undergo spontaneous emission and relax to the ground state. Using this parameterisation we can express the amplitude damping channel as,
\begin{align}
\mathcal{E}_t^\mathrm{relax}(\hat\rho) = e^{-t/T_1}\hat\rho + (1-e^{-t/T_1})\ket{0}\bra{0},
\end{align}
for which the output state is of the form,
\begin{align}
\hat\rho_t = \left(\begin{matrix}{}
1 + (\alpha-1) e^{-t/T_1} & \gamma e^{-t/T_1} \\
\gamma^* e^{-t/T_1} & \beta e^{-t/T_1}
\end{matrix}\right).
\end{align}

>>>>

Consider an even-parity cat state, as per Eq.~(\ref{eq:cat_state_enc}). Subjecting this to a loss channel yields the mixed state,
\begin{align}
&\hat\rho_\mathrm{loss} = \mathcal{E}_\eta^\mathrm{loss}(\ket{\mathrm{cat}_+(\alpha)}\bra{\mathrm{cat}_+(\alpha)}) \nonumber\\
&= {\mathcal{N}_+}^2 [\mathcal{E}_\eta^\mathrm{loss}(\ket{\alpha}\bra{\alpha}) + \mathcal{E}_\eta^\mathrm{loss}(\ket{-\alpha}\bra{-\alpha}) \nonumber\\
&+ \mathcal{E}_\eta^\mathrm{loss}(\ket{-\alpha}\bra{\alpha}) + \mathcal{E}_\eta^\mathrm{loss}(\ket{\alpha}\bra{-\alpha})]\nonumber\\
&= {\mathcal{N}_+}^2[\ket{\eta\alpha}\bra{\eta\alpha} + \ket{-\eta\alpha}\bra{-\eta\alpha}\nonumber\\
&+e^{-2|(1-\eta)\alpha|^2}(\ket{\eta\alpha}\bra{-\eta\alpha}+\ket{-\eta\alpha}\bra{\eta\alpha})].
\end{align}
Now it's evident that the off-diagonal terms (i.e those representing coherence) accumulate a factor of,
\begin{align}
C=e^{-2|(1-\eta)\alpha|^2},	
\end{align}
which rapidly asymptotes to zero for large $\alpha$ with any \mbox{$\eta<1$}, as shown in Fig.~\ref{fig:cat_decoherence}.

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{cat_decoherence}
	\caption{Coherence factor in an even-parity cat state subject to decoherence via loss, as a function of efficiency $\eta$, and the coherent amplitude $\alpha$.}\label{fig:cat_decoherence}
\end{figure}

@@

A qubit dephasing channel is often quoted in terms of its $T_2$-time, a characteristic time for dephasing to occur under continuous time-evolution. Specifically, the probability of no dephasing occurring scales as,
\begin{align}
p_\mathrm{no\,error} = e^{-t/T_2},	
\end{align}
yielding a the equivalent dephasing channel,
\begin{align}
\mathcal{E}_t^\mathrm{dephasing}(\hat\rho) = e^{-t/T_2} \hat\rho + \frac{1}{2}(1-e^{-t/T_2})(\hat\rho + \hat{Z}\hat\rho\hat{Z}),
\end{align}
as shown in Fig.~\ref{fig:T2_time}. For a qubit density matrix,
\begin{align}
	\hat\rho = \left(\begin{matrix}{}
 \alpha & \gamma \\
 \gamma^* & \beta
\end{matrix}\right),
\end{align}
this is equivalent to adding a factor of $e^{-t/T_2}$ to the two off-diagonal (coherence) elements,
\begin{align}
	\hat\rho_t = \left(\begin{matrix}{}
 \alpha & e^{-t/T_2}\gamma \\
 e^{-t/T_2}\gamma^* & \beta
\end{matrix}\right).
\end{align}

@@

The degree of amplitude damping is often quoted in terms of a channel's $T_1$-time, characterising the expected time for the excited state to undergo spontaneous emission and relax to the ground state. Using this parameterisation we can express the amplitude damping channel as,
\begin{align}
\mathcal{E}_t^\mathrm{relax}(\hat\rho) = e^{-t/T_1}\hat\rho + (1-e^{-t/T_1})\ket{0}\bra{0},
\end{align}
for which the output state is of the form,
\begin{align}
\hat\rho_t = \left(\begin{matrix}{}
1 - (1-\alpha) e^{-t/T_1} & \gamma e^{-t/T_1} \\
\gamma^* e^{-t/T_1} & \beta e^{-t/T_1}
\end{matrix}\right).
\end{align}
